Figures and Tables

### 2021-01-08 paper/figures_tables.Rmd
not liking Rmd version much
Fine, doing figures in rmd

```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
library(purrr)
library(fitdistrplus)
library(ggpubr)

@@

# Layout of steps of one simulation run

# Figure with variation for parameter estimates

# Table: Info criteria for family and individual levels

# Facetted plot for seed dispersal distances

# Density figures from which step and grt are sampled from

>>>>

```{r movementdensity, fig.width=6, fig.height=2}

load("paper/simple_exp_runs.RData")

library(ggplot2)
library(dplyr)

# Figure for movement rates at the three levels

rates <- data.frame(level = "null", movrate = null_moverate$movrate[1]) %>%
  bind_rows(., indiv_moverate %>%
              rename(level = Bird_ID)) %>%
  bind_rows(., fam_moverate %>%
              rename(level = fam_g)) %>%
  mutate(model = ifelse(level == "null", "Null",
                        ifelse(level %in% paste0("f", 1:7), "Family", "Individual")))

n <- 1000
dens_rates <- NULL
for(i in 1:length(rates$level)) {
  dens_exp <- rexp(n, rate = 1/rates$movrate[i])

  out <- data.frame(level = rates$level[i], model = rates$model[i], value = dens_exp)
  dens_rates <- rbind.data.frame(dens_rates, out)
}

dens_rates %>%
  mutate(model = factor(model, levels = c("Null", "Individual", "Family"))) %>%
  ggplot(., aes(x = value, group = level, color = model)) +
  facet_wrap(~model) +
  geom_density() +
  scale_color_manual(values = c("red", "grey", "black"), guide = "none") +
  theme_bw() + labs(x = "Distance in meters per minute") +
  #coord_cartesian(xlim = c(100, 300), ylim = c(0, 0.0025))+
  NULL
```

```{r grt, fig.width=3, fig.height=2}

n <- 10000
grt_dens <- data.frame(seq = 1:n, dat = (rgamma(n, shape = 4, scale = 5) + 8))
grt_data <- data.frame(time = round(sample(grt_dens$dat, 5)), seq = 1:5)
tt <- max(grt_data$time)
ggplot(grt_dens, aes(x = dat)) +
  geom_density() + 
  geom_point(data = grt_data, aes(x = time, y = 0)) +
  theme_bw() + labs(x = "Time in minutes")

@@
